---
title: "Twitter communication after Triell"
author: "Lorenz Biberstein"
date: "13 9 2021"
output: html_document
---

```{r}
library(rtweet)
```


```{r setup, include = TRUE}
# Global setup for all R chunks in this file
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(include = TRUE) # for now all R chunks are included, can be taken out here later
```


# Chapter 1: Getting twitter data

```{r twitter_token}
source("twitter_token.R", local = knitr::knit_global())
# load twitter tokens from separate file (not shared on github for privacy reasons)
```

```{r get_twitter_data}
triell <- search_tweets("Triell", # Search tweets with search phrase "Triell"
                        n=10, # get 10 tweets
                        include_rts=FALSE, # do not include retweets
                        lang="de" # Only tweets from Twitter users with German language
                        )
```


```{r save_to_disk}
# Save data as csv
write_as_csv(triell, "data/triell_2021-09-14.csv", prepend_ids = TRUE, na = "", fileEncoding = "UTF-8")
```


# Chapter 2


This is some text.

These are bullet points:

-   Lorem
-   Ipsum
  - etc.
  
This is an enumeration:

1. First line
2. Second line
3. Third line

This is how you emphasise text: _emphasised_. And this his how to write in bold: **bold**.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

# Chapter 3

Trying github
